### 2016-03-21 papers.tex
papers.tex: Move all page numbers to the same height
We won't be making use of the intended workaround of moving the page numbers to
cover those on submission originals; instead, I'll manually redact the current
page numbers with Acrobat prior to sending it for publication. In future years,
we should fix the main-matter.tex code to extend vboxes upward and cover old
numbering systems.

\addtrack{Half-track}{Crypticography}
\addpaper
	{Cryptographically secure page numbering in \LaTeX}
	{William Gunther and Brian Kell}
	{cryptography, hashing, LaTeX, macros, page numbers, security, SHA-256}
	{SIGBOVIK_2016_paper_18}
	{-2cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper18eval}{-1.45cm}
\addpaper
	{Random seed generation}
	{Alexander R.\ Frieder}
	{random, seed, encryption, complexity, am, I, even, supposed, to, fill, this, out, what, amI, doing, ?}
	{SIGBOVIK_2016_paper_1}
	{0cm}
	{}

\addtrack{Full track}{Safety Schools of Thought}
\addpaper
	{Reducing the trusted constituent base with the LCF approach: Hillary, the next 700 elections}
	{Brandon Bohrer, Sol Boucher, and Jos Valdivida}
	{illogical, logic, Hillary, elections, congressional, fuckery, robustness, constituents, unrest, pork-barreling, curtain-closing}
	{SIGBOVIK_2016_paper_25}
	{0cm}
	{}
\addpaper
	{Unprl: Nuprl proof re-evaluation logic}
	{Ryan Kavanagh}
	{proof assistant, Nuprl, The Wizard of Oz, artificial artificial intelligence}
	{SIGBOVIK_2016_paper_11}
	{0cm}
	{}
\addpaper
	{Type-safe friends will never hurt you}
	{Brandon Bohrer}
	{friendship logic, friends, office mates, Cwelf}
	{SIGBOVIK_2016_paper_9}
	{-2cm}
	{}
\addreview{review9}{0cm}

\addtrack{Rototiller track}{Overcomplexity Theory}
\addpaper
	{The computational complexity of Chinese and Italian noodle making}
	{Daniel M.\ Berry and Luisa Mich}
	{algorithm, Chinese mian, computational complexity, Italian pasta, noodle}
	{SIGBOVIK_2016_paper_2}
	{0cm}
	{}
\addreview{paper2review}{0cm}
\addpaper
	{Which ITG stepcharts are turniest?}
	{Ben Blum}
	{in, the, groove}
	{SIGBOVIK_2016_paper_12}
	{0cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper12eval}{-1.45cm}

@@

\addtrack{Footpath track}{HyperLink to DnD}
\addpaper
	{The glEnd() of Zelda}
	{Dr.\ Tom Murphy VII Ph.D.}
	{small keys, boss keys, dungeon keys}
	{SIGBOVIK_2016_paper_16}
	{-1.1cm}
	{}
\addpaper
	{Student success and sorrow: The determination of professor alignment and its effects on students}
	{D.\ Daly and E.\ Binns}
	{professors, academia, alignment}
	{SIGBOVIK_2016_paper_24}
	{-1.9cm}
	{}

\addtrack{Garbage track}{Reduce, Reuse, Recycle}
\addpaper
	{PRESS RELEASE: FOR IMMEDIATE WORLDWIDE RELEASE}
	{Nicholas Fudala and Chester Francis}
	{editors note, this didnt seem very important, so we sat on it for 2 years, with love, the ach committee for retrocausal publication impact}
	{SIGBOVIK_2016_paper_17}
	{0cm}
	{}
\addpaper
	{Pittsburgh is a grid}
	{Stefan Muller}
	{Pittsburgh, grids, unnecessary integrals, computational geography}
	{SIGBOVIK_2016_paper_10}
	{-0.3cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper10eval}{-1.35cm}

\addtrack{Oversized track}{How (Over)fitting}
\addpaper
	{Reordering snacks is effective and just}
	{Dr.\ Tom Murphy VII Ph.D.}
	{snacking, permutations, comestability theory}
	{SIGBOVIK_2016_paper_8}
	{-1.2cm}
	{}
\addpaper
	{0-order Non-linear ordinary differential equations}
	{Oscar I.\ Hernandez and Daniel J.\ Packer}
	{ordinary differential equations, non-linear, nonhomo}
	{SIGBOVIK_2016_paper_5}
	{0cm}
	{}
\addpaper
	{Deep spreadsheets with ExcelNet}
	{David Fouhey and Daniel Maturana}
	{deep learning, Excel, LibreOffice, convolutional neural network, spreadsheet}
	{SIGBOVIK_2016_paper_21}
	{0cm}
	{}
\addpaper
	{Sniffing for meaning: Defining and maximizing the signal-to-nose ratio}
	{Josh Cox}
	{signal, nose, ratio, sniff, smell, scent}
	{SIGBOVIK_2016_paper_22}
	{0cm}
	{}
\addreview{paper22review}{-1.45cm}

\addtrack{Cattle track}{Higher-order Research}
\addpaper
	{On the topic of "um..."}
	{Timothy J.\ Parenti}
	{um, best, paper}
	{SIGBOVIK_2016_paper_20}
	{-0.55cm}
	{}
\addreview{review-bestpaper}{0cm}
\addpaper
	{SMACK: When research in algorithms goes around in circles}
	{Patrick Lin and Weishuang Linda Xu}
	{algorithms, collider, particle physics}
	{SIGBOVIK_2016_paper_4}
	{-2cm}
	{}
\addreview{review-smack}{0cm}
\addpaper
	{A look into the mind of the modern graduate student via telephonic obfuscation}
	{Erik Harpstead \textit{et al.}}
	{comestibility theory, telephonic obfuscation, computer human interaction}
	{SIGBOVIK_2016_paper_6}
	{0cm}
	{}
\addpaper
	{Dinner grant renewal request}
	{From Dr.\ Angus McNabb III to Jim McCann}
	{dinner, dog pictures, naps, napping, nap time, sleeping}
	{SIGBOVIK_2016_paper_14}
	{0cm}
	{}
\addpaper
	{Ode to reviewer two}
	{Anonymous}
	{ode, double-blind review, false politeness, landslide}
	{SIGBOVIK_2016_paper_7}
	{0cm}
	{}

>>>>

\addtrack{Half-track}{Crypticography}
\addpaper
	{Cryptographically secure page numbering in \LaTeX}
	{William Gunther and Brian Kell}
	{cryptography, hashing, LaTeX, macros, page numbers, security, SHA-256}
	{SIGBOVIK_2016_paper_18}
	{0cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper18eval}{0cm}
\addpaper
	{Random seed generation}
	{Alexander R.\ Frieder}
	{random, seed, encryption, complexity, am, I, even, supposed, to, fill, this, out, what, amI, doing, ?}
	{SIGBOVIK_2016_paper_1}
	{0cm}
	{}

\addtrack{Full track}{Safety Schools of Thought}
\addpaper
	{Reducing the trusted constituent base with the LCF approach: Hillary, the next 700 elections}
	{Brandon Bohrer, Sol Boucher, and Jos Valdivida}
	{illogical, logic, Hillary, elections, congressional, fuckery, robustness, constituents, unrest, pork-barreling, curtain-closing}
	{SIGBOVIK_2016_paper_25}
	{0cm}
	{}
\addpaper
	{Unprl: Nuprl proof re-evaluation logic}
	{Ryan Kavanagh}
	{proof assistant, Nuprl, The Wizard of Oz, artificial artificial intelligence}
	{SIGBOVIK_2016_paper_11}
	{0cm}
	{}
\addpaper
	{Type-safe friends will never hurt you}
	{Brandon Bohrer}
	{friendship logic, friends, office mates, Cwelf}
	{SIGBOVIK_2016_paper_9}
	{0cm}
	{}
\addreview{review9}{0cm}

\addtrack{Rototiller track}{Overcomplexity Theory}
\addpaper
	{The computational complexity of Chinese and Italian noodle making}
	{Daniel M.\ Berry and Luisa Mich}
	{algorithm, Chinese mian, computational complexity, Italian pasta, noodle}
	{SIGBOVIK_2016_paper_2}
	{0cm}
	{}
\addreview{paper2review}{0cm}
\addpaper
	{Which ITG stepcharts are turniest?}
	{Ben Blum}
	{in, the, groove}
	{SIGBOVIK_2016_paper_12}
	{0cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper12eval}{0cm}

@@

\addtrack{Footpath track}{HyperLink to DnD}
\addpaper
	{The glEnd() of Zelda}
	{Dr.\ Tom Murphy VII Ph.D.}
	{small keys, boss keys, dungeon keys}
	{SIGBOVIK_2016_paper_16}
	{0cm}
	{}
\addpaper
	{Student success and sorrow: The determination of professor alignment and its effects on students}
	{D.\ Daly and E.\ Binns}
	{professors, academia, alignment}
	{SIGBOVIK_2016_paper_24}
	{0cm}
	{}

\addtrack{Garbage track}{Reduce, Reuse, Recycle}
\addpaper
	{PRESS RELEASE: FOR IMMEDIATE WORLDWIDE RELEASE}
	{Nicholas Fudala and Chester Francis}
	{editors note, this didnt seem very important, so we sat on it for 2 years, with love, the ach committee for retrocausal publication impact}
	{SIGBOVIK_2016_paper_17}
	{0cm}
	{}
\addpaper
	{Pittsburgh is a grid}
	{Stefan Muller}
	{Pittsburgh, grids, unnecessary integrals, computational geography}
	{SIGBOVIK_2016_paper_10}
	{0cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper10eval}{0cm}

\addtrack{Oversized track}{How (Over)fitting}
\addpaper
	{Reordering snacks is effective and just}
	{Dr.\ Tom Murphy VII Ph.D.}
	{snacking, permutations, comestability theory}
	{SIGBOVIK_2016_paper_8}
	{0cm}
	{}
\addpaper
	{0-order Non-linear ordinary differential equations}
	{Oscar I.\ Hernandez and Daniel J.\ Packer}
	{ordinary differential equations, non-linear, nonhomo}
	{SIGBOVIK_2016_paper_5}
	{0cm}
	{}
\addpaper
	{Deep spreadsheets with ExcelNet}
	{David Fouhey and Daniel Maturana}
	{deep learning, Excel, LibreOffice, convolutional neural network, spreadsheet}
	{SIGBOVIK_2016_paper_21}
	{0cm}
	{}
\addpaper
	{Sniffing for meaning: Defining and maximizing the signal-to-nose ratio}
	{Josh Cox}
	{signal, nose, ratio, sniff, smell, scent}
	{SIGBOVIK_2016_paper_22}
	{0cm}
	{}
\addreview{paper22review}{0cm}

\addtrack{Cattle track}{Higher-order Research}
\addpaper
	{On the topic of "um..."}
	{Timothy J.\ Parenti}
	{um, best, paper}
	{SIGBOVIK_2016_paper_20}
	{0cm}
	{}
\addreview{review-bestpaper}{0cm}
\addpaper
	{SMACK: When research in algorithms goes around in circles}
	{Patrick Lin and Weishuang Linda Xu}
	{algorithms, collider, particle physics}
	{SIGBOVIK_2016_paper_4}
	{0cm}
	{}
\addreview{review-smack}{0cm}
\addpaper
	{A look into the mind of the modern graduate student via telephonic obfuscation}
	{Erik Harpstead \textit{et al.}}
	{comestibility theory, telephonic obfuscation, computer human interaction}
	{SIGBOVIK_2016_paper_6}
	{0cm}
	{}
\addpaper
	{Dinner grant renewal request}
	{From Dr.\ Angus McNabb III to Jim McCann}
	{dinner, dog pictures, naps, napping, nap time, sleeping}
	{SIGBOVIK_2016_paper_14}
	{0cm}
	{}
\addpaper
	{Ode to reviewer two}
	{Anonymous}
	{ode, double-blind review, false politeness, landslide}
	{SIGBOVIK_2016_paper_7}
	{0cm}
	{}
